Longitudinal Principal Manifold Estimation

### 2024-06-25 paper/main.tex

Previous work on longitudinal dimension reduction methods has primarily focused on linear approaches, such as the longitudinal PCA method proposed by \cite{kinsonLongitudinalPrincipalComponent2020} and longitudinal functional PCA proposed by \cite{greven2011longitudinal}. As for nonlinear methods, \cite{wolzManifoldLearningBiomarker2010a} used Laplacian eigenmaps to incorporate longitudinal information when reducing neuroimaging data to lower dimensional space. However, parameterizations for baseline images and longitudinal image differences were estimated separately while we seek to parameterize them simultaneously. In addition, \cite{louisRiemannianGeometryLearning2019} used a deep learning-based approach to learn Riemannian manifolds in the context of disease progression modeling. However, this approach relies on modeling assumptions specific to the application, and the deep learning methodology used imposes costs in terms of computational requirements and interpretability.

@@

\bibliographystyle{plainnat}
\bibliography{references}

>>>>

Previous work on longitudinal dimension reduction methods has primarily focused on linear approaches, such as the longitudinal PCA method proposed by \cite{kinsonLongitudinalPrincipalComponent2020} and longitudinal functional PCA proposed by \cite{greven2011longitudinal}. As for nonlinear methods, \cite{wolzManifoldLearningBiomarker2010} used Laplacian eigenmaps to incorporate longitudinal information when reducing neuroimaging data to lower dimensional space. However, parameterizations for baseline images and longitudinal image differences were estimated separately while we seek to parameterize them simultaneously. In addition, \cite{louisRiemannianGeometryLearning2019} used a deep learning-based approach to learn Riemannian manifolds in the context of disease progression modeling. However, this approach relies on modeling assumptions specific to the application, and the deep learning methodology used imposes costs in terms of computational requirements and interpretability.

@@

\bibliographystyle{agsm}
\bibliography{references}
